---
title: "random data"
author: "Natasha"
date: "10/7/2018"
output: html_document
---

```{r}
library(pacman)
p_load_gh("trinker/wakefield")
```


sample of items you can put into a dataset 

```{r}
race(n=10)
sex(10)
likert_7(10)
gpa(10)
```



use the r_data_frame to combine the varaibles into a dataset 

```{r}
set.seed(10)

r_data_frame(
    n = 500,
    id,
    race,
    age,
    sm,
    ma,
    Start = hour,
    End = hour,
    iq,
    height,
    died
)
```



The original blog post provided a means for adding missing values. wakefield keeps this alive and adds more flexibility. It is no longer a part of the data generation process but a function, r_na, that is called after the data set has been generated. The user can specify which columns to add NAs to. By default column 1 is excluded. This works nicely within a dplyr/magrittr pipe line. Note: dpyr has an id function ad well so the prefix wakedfield:: must be used for id.

```{r}
p_load(dplyr)
set.seed(10)

r_data_frame(
    n = 30,
    id,
    state,
    month,
    sat,
    minute,
    iq,
    zip_code,
    year,
    Scoring = rnorm,
    Smoker = valid,
    sentence
) %>%
    r_na(prob=.25)

```

There’s still a default data set function, r_data, in case the functionality of the original random data generation function is missed or if you’re in a hurry and aren’t too picky about the data being generated.

```{r}
set.seed(10)

r_data(1000)
```

make columns that are correlated or any function of another column.

```{r}
p_load(dplyr)
set.seed(10)

dplyr::data_frame(
    x = 1:10,
    y = x + rnorm(10)
)
```


The user can use the modular variable functions inside of dplyr::data_frame and have this functionality but the column name and n must explicit be passed to each variable.

```{r}
set.seed(10)

dplyr::data_frame(
    ID = wakefield::id(n=10),
    Smokes = smokes(n=10),
    Sick = ifelse(Smokes, sample(5:10, 10, TRUE), sample(0:4, 10, TRUE)),
    Death = ifelse(Smokes, sample(0:1, 10, TRUE, prob = c(.2, .8)), sample(0:1, 10, TRUE, prob = c(.7, .3)))
)
```

## Export data to excel

```{r}
library(xlsx)
write.xlsx(mydata, "c:/mydata.xlsx")   ##### DOESNT WORK #########
```


```{r}
write.csv(dataset, "filename.csv")
```



## to SPSS

```{r}
# write out text datafile and
# an SPSS program to read it
library(foreign)
write.foreign(mydata, "c:/mydata.txt", "c:/mydata.sps",   package="SPSS")
```

## To SAS

```{r}
# write out text datafile and
# an SAS program to read it
library(foreign)
write.foreign(mydata, "c:/mydata.txt", "c:/mydata.sas",   package="SAS")
```

## To a Tab delimited text file 

```{r}
write.table(mydata, "c:/mydata.txt", sep="\t")
```


```{r}
church <- r_data_frame(
    n= 125,
    id,
    Scoring= round(digits=0, rnorm(n=125, mean=5, sd=1)),
    Scoring= round(digits=0, rnorm(n=125, mean=4, sd=1)),
    age(x=19:32),
    sex,
    race
    )
```

 



```{r}
depillo <- r_data_frame(
  n=150,
  id,
  likert(n=150),
  likert(n=150),
  race,
  sex(n=150, x="female"),
  answer(n=150, x= c("track", "soccer")),
  Scoring= rnorm(mean=5, sd=1),
  Scoring= rnorm(mean=4, sd=1)
)
```

```{r}
dickerson <-r_data_frame(
  n=20,
  id,
  likert(n=20),
  race,
  sex,
  speed_mph(n=20, mean=55, sd=10, min=35, max=NULL, digits=0, name="Speed sector a"),
  time_stamp(),
  speed_mph(n=20, mean=55, sd=10, min=35, max=NULL, digits=0, name="Speed sector b"),
  time_stamp(),
  speed_mph(n=20, mean=55, sd=10, min=35, max=NULL, digits=0, name="Speed sector c"),
  time_stamp()
  
)
```

```{r}
gallaher <- r_data_frame(
  n=150,
  id,
  sex_inclusive(n=150, x= c("Male", "Female", "Intersex")),
  race,
  age(x=18:40),
  likert(n=150, x= c(1, 2, 3, 4, 5)),
  likert(n=150, x= c(1, 2, 3, 4, 5)),
  likert(n=150, x= c("1", "2", "3", "4"), prob= NULL, name="Group"),
  answer(n=150, x= c("1", "2")),
  answer(n=150, x= c("1", "2")),
  answer(n=150, x= c("1", "2"))
  
)
```

```{r}
gillmore <- r_data_frame(
  n=70,
  id,
  sex,
  race,
  group(n=70, x= c("control", "treatment"), name="group"),
  likert_7(n=70, x = c("0", "1", "2", "3",
      "4"), prob = NULL,
      name = "Baseline"),
  likert_7(n=70, x = c("0", "1", "2", "3",
      "4"), prob = NULL,
      name = "PSS_1"),
  likert_7(n=70, x = c("0", "1", "2", "3",
      "4"), prob = NULL,
      name = "PSS_2"),
  likert_7(n=70, x = c("0", "1", "2", "3",
      "4"), prob = NULL,
      name = "PSS_4"),
  likert_7(n=70, x = c("0", "1", "2", "3",
      "4"), prob = NULL,
      name = "PSS_4"),
  likert_7(n=70, x = c("0", "1", "2", "3",
      "4"), prob = NULL,
      name = "PSS_5"),
  likert_7(n=70, x = c("0", "1", "2", "3",
      "4"), prob = NULL,
      name = "PSS_6")
)
```

```{r}
gipson <- r_data_frame(
  n=100,
  id,
  sex,
  race,
  age(x=19:32),
  Scoring= rnorm(n=100, mean=40, sd=1),
  Scoring= rnorm(n=100, mean=45, sd=1)
)
```

```{r}
hall <- r_data_frame(
  n=63,
  id,
  sex,
  education,
  race,
  age(x=16:35),
  answer(n=63, x= c("control", "synesthetes")),
  Scoring= rnorm,
  Scoring= rnorm,
  likert()
)
```


```{r}
hanley <-r_data_frame(
  n=7798,
  id,
  sex,
  age(16:19),
  race,
  gpa,
  Scoring=rnorm(n=7798, mean=8, sd=1)
)
```

```{r}
hollomon <-r_data_frame(
  n=20,
  id,
  age(18:23),
  sex,
  race,
  likert(),
  Scoring=rnorm(n=20, mean=75, sd=1),
  Scoring=rnorm(n=20, mean=88, sd=1)
)
```

```{r}
mcelhaney <-r_data_frame(
  n=28,
  id,
  age(4:5),
  sex,
  race,
  likert(),
  Scoring= rnorm(n=28, mean=40, sd=1),
  Scoring= rnorm(n=28, mean=45, sd=1),
  answer(n=28, x= c("excell", "home"))
)
```

```{r}
mckeel <-r_data_frame(
  n=100,
  id,
  age(18:24),
  race,
  sex,
  likert(),
  Scoring= rnorm(n=100, mean=48, sd=1)
  
)
```

```{r}
riddle <-r_data_frame(
  n=100,
  id,
  age(3:18),
  race,
  sex,
  Scoring= round(digits=0, rnorm(n=100, mean=5, sd=1)),
  Scoring= rnorm(n=100, mean=4, sd=1)
  
)
```

```{r}
sexton <-r_data_frame(
  n=60,
  id,
  age(3:7),
  race,
  sex,
  likert(),
  Scoring= rnorm(n=60, mean=767, sd=2),
  Scoring= rnorm(n=60, mean=790, sd=2)
  
)
```

```{r}
smart <-r_data_frame(
  n=100,
  id,
  age,
  race,
  sex,
  likert(),
  likert(),
  likert(),
  likert(),
  answer(n=100, x= c("oldest", "middle", "youngest"))
  
)
```

```{r}
stephens <-r_data_frame(
  n=100,
  id,
  age(12:14),
  race,
  sex,
  Scoring= rnorm(n=100, mean=790, sd=2),
  Scoring= rnorm(n=100, mean=790, sd=2)
)
```

```{r}
woodward <-r_data_frame(
  n=100,
  id,
  age(18:24),
  race,
  sex,
  likert()
)
```


```{r}
write.csv(woodward, "woodward.csv")

```

```{r}
write.csv(church, "church.csv")
write.csv(depillo, "depillo.csv")
write.csv(dickerson, "dickerson.csv")
write.csv(gallaher, "gallaher.csv")
write.csv(gillmore, "gillmore.csv")
write.csv(gipson, "gipson.csv")
write.csv(hanley, "hanley.csv")
write.csv(hollomon, "hollomon.csv")
write.csv(mcelhaney, "mcelhaney.csv")
write.csv(mckeel, "mckeel.csv")
write.csv(riddle, "riddle.csv")
write.csv(sexton, "sexton.csv")
write.csv(smart, "smart.csv")
write.csv(stephens, "stephens.csv")
write.csv(hall, "hall.csv")
```



#### 001 datasets

```{r}
alu <-r_data_frame(
  n=100,
  id,
  race,
  age(18:50),
 Scoring= round(digits=0, rnorm(n=100, mean=2.3, sd=1)),
  likert_5(n=100, x = c("0", "1", "2", "3", "4",
      "5"), prob = NULL, name = "Likert"),
  likert_5(n=100, x = c("0", "1", "2", "3",
      "4"), prob = NULL, name = "Likert")
)

```


```{r}
arnett <- r_data_frame(
  n=360,
  id,
  race,
  sex,
  age(17:19),
  gpa,
  Scoring= round(digits=0, rnorm(n=360, mean=5, sd=1)),
 23,
  gpa,
  Scoring= round(digits=2, rnorm(n=360, mean=.76, sd=.8)),
  Scoring= round(digits=0, rnorm(n=360, mean=88, sd=2))
)
```

```{r}
gillish <- r_data_frame(
  n=100,
  id=("treatment"),
  race,
  sex,
  age(13:18),
  Scoring= round(digits=0, rnorm(n=100, mean=5, sd=1)),
  Scoring= round(digits=2, rnorm(n=100, mean=50, sd=.8)),
  Scoring= round(digits=2, rnorm(n=100, mean=23, sd=.5))
)
```

```{r}
gillish_control <- r_data_frame(
  n=10,
  id=("control"),
  race,
  sex,
  age(13:18),
  Scoring= round(digits=0, rnorm(n=100, mean=5, sd=1)),
  Scoring =round(digits=0, rnorm(n=10, mean=6, sd=1))
)
```

```{r}
a_gillish_baker_powers_murr <-cbind(gillish, gillish_control)
```


```{r}
baker_other <- r_data_frame(
  n=150,
  group(n=150, x= c("Control", "Treatment"), name="group"),
  race,
  sex,
  age(13:18),
  Scoring= round(digits=0, rnorm(n=150, mean=5, sd=1)),
  Scoring= round(digits=2, rnorm(n=150, mean=50, sd=.8)),
  Scoring= round(digits=2, rnorm(n=150, mean=23, sd=.5))
)
```



```{r}
blakley_freeman <-r_data_frame(
  n=20,
  group(n=20, x= c("Control", "Treatment"), name="group"),
  id,
  race,
  age(15:18),
  Scoring= round(digits=0, rnorm(n=20, mean=6, sd=1)),
  Scoring= round(digits=2, rnorm(n=20, mean=125, sd=2))
)
```

```{r}
gibson <-r_data_frame(
  n=1400,
  group(n=1400, x= c("College", "Other"), name="group"),
  id,
  sex,
  race(n=1400, c("White", "Black"), prob= c(.5,.5), name= "race"),
  age(18:45),
  Scoring= round(digits=0, rnorm(n=1400, mean=8, sd=2))
)
```

```{r}
gunter <-r_data_frame(
  n=300,
  race,
  sex,
  group(n=300, x= c("control", "treatment"), name="group"),
  age(15:25),
  Scoring= round(digits=0, rnorm(n=300, mean=5, sd=.8))
)
```



########
```{r}
hill <-r_data_frame(
  n=100,
  id,
  race,
  sex,
  age(40:65),
  likert_7(n=100, x = c("1", "2", "3", "4",
      "5", "6", "7"), prob = NULL,
      name = "Likert"),
  Scoring= round(digits=0, rnorm(n=100, mean=3, sd=1)),
 likert_7(n=100, x = c("0", "1", "2", "3",
      "4", "5", "6", "7", "8"), prob = NULL,
      name = "Likert")
)
```

```{r}
hollandsworth_welch <-r_data_frame(
  n=500,
  id,
  sex,
  race,
  age(18:23),
  gpa,
  Scoring= round(digits=0, rnorm(n=500, mean=13, sd=2)),
  Scoring= round(digits=0, rnorm(n=500, mean=4, sd=.6)),
  gpa,
  Scoring= round(digits=0, rnorm(n=500, mean=11, sd=2)),
  Scoring= round(digits=0, rnorm(n=500, mean=3, sd=.6))
  )
```

```{r}
jordan_sharpe <-r_data_frame(
  n=533,
  id,
  sex,
  race,
  age(14:18),
  Scoring= round(digits=0, rnorm(n=533, mean=76, sd=2)),
  Scoring= group(n=533, x= c("cell phone", "computer"), name="group"), round(digits=0, rnorm(n=533, mean=22, sd=2))
)
```

```{r}
woodring <- r_data_frame(
 n=500,
 id,
 race,
 sex,
 age(18:23),
 Scoring= round(digits=0, rnorm(n=500, mean=23, sd=2)),
 Scoring= round(digits=0, rnorm(n=500, mean=25, sd=2))
)
```

```{r}
write.csv(woodring, "woodring.csv")
write.csv(jordan_sharpe, "jordan_sharpe.csv")
write.csv(hollandsworth_welch, "hollandsworth_welch.csv")
write.csv(hill, "hill.csv")
write.csv(gunter, "gunter.csv")
write.csv(gibson, "gibson.csv")
write.csv(blakley_freeman, "blakley_freeman.csv")
write.csv(baker_other, "baker_other.csv")
write.csv(a_gillish_baker_powers_murr, "a_gillish_baker_powers_murr.csv")
write.csv(arnett, "arnett.csv")
write.csv(alu, "alu.csv")
```

